CP-SSA

### 2025-02-28 Code/R/Research/CP-SSA.Rmd
Comparing all methods on pulse signal.

```{r enable progressr, eval = FALSE}
# This command should be executed in R console, not as a chunk
# Otherwise it fails
progressr::handlers(global = TRUE)
```

@@

@@

pulse_rmse_L_res <- cbind(tens_dims, pulse_rmse_L(R))
save(pulse_rmse_L_res, file = "./Research/comp_results/cp_pulse_L.RData")
pulse_rmse_L_res[order(pulse_rmse_L_res[, 4], decreasing = FALSE), ] |> head() |> print()
```

@@

>>>>

```{r enable progressr, eval = FALSE}
# This commands should be executed in R console, not as a chunk
# Otherwise they fail
progressr::handlers(global = TRUE)
progressr::handlers("progress")
```

@@

ls <- seq(from = 240,
          to = (N + 1) %/% 2,
          by = 120)
Js <- seq(from = 120, to = max(ls) - max.r + 1, by = 120)

correct_dims <- which(outer(ls, Js, (\(l, j) ifelse((l >= j) &
                                                      (N %% l == 0) &
                                                      (l - j + 1 <= j) &
                                                      (l - j + 1 >= max.r), TRUE, FALSE
))), arr.ind = TRUE)

@@

pulse_rmse_L_res <- cbind(tens_dims, pulse_rmse_L(R))
save(pulse_rmse_L_res, file = "./Research/comp_results/cp_pulse_L.RData")
pulse_rmse_L_res[order(pulse_rmse_L_res[, 4], decreasing = FALSE), ] |> head() |> print()
# 1200  960 241 0.03489966
```

@@

### Comparing all
```{r}
N <- 6000
times <- seq(from = 0,
             to = 1,
             length.out = N)
freq <- 50
freq2 <- 10
amp_period <- 5
s <- 2 * exp(-0.2 * pi * freq * times[1:(N %/% amp_period)]) * sin(2 * pi * freq * times) +
  sin(2 * pi * freq2 * times)

L_ssa <- 1920
L_mssa <- 840
L_cp <- c(1200, 960)
L_homssa <- 360
groups_ssa <- list(1:32)
groups_mssa <- list(1:2, 3:4)
groups_cp <- list(c(1, 3), c(2, 4))
groups_homssa <- list(1:2, 3:4)
groups3 <- list(1:3, 1:3)
sd <- 0.5
R <- 1000
tol <- 1e-7
max_iter = 25
cp_span = "last"

pulse_all_rmse <- function(R) {
  p <- progressor(R)
  future_replicate(R, {
    p()
    compare_all_ssa()
  }, simplify = "array", future.seed = 5) |> rowMeans() |> sqrt()
}

pulse_all_rmse_comp_res <- pulse_all_rmse(R)
save(
  L_ssa,
  L_mssa,
  L_cp,
  L_homssa,
  groups_ssa,
  groups_mssa,
  groups_cp,
  groups_homssa,
  groups3,
  pulse_all_rmse_comp_res,
  file = "./Research/comp_results/all_pulse_comp.RData"
)
print(pulse_all_rmse_comp_res)
```
